---
title: "FactBook generation wrapper"
author: "Dan Deabler"
date: "2025-03-27"
output: html_document
---

# This is wrapper script that executes all specific FactBook section scripts (e.g. FactBook_generation_Enrollment.R)


# NOTES:
# 1). This file acts as a wrapper for generating the North Carolina Central University (NCCU) Factbook and is the only file that needs to be executed.
# 2). Raw data files cannot be provided due to the sensitivity of the institutional data and therefore this repository cannot be used; rather, it demonstrates the steps taken for generating the publication.
# 3). University Financial information (Factbook_generation_University_Finances.R) with format `(paste0(university_finances_dir, "NCCU_FY_", year, "-", year+1, ".xlsx")` (e.g. NCCU_FY_2023-2024).


# Set global variables
```{r}

username <- "ddeabler"
year <- 2023 # This specifies both the Fall semester (Fall 2023) and the academic year (2023-2024).
data_dir <- "O:/OIRA/IR/Dan/Data Cleanup/" # Where data source files are stored
intermediary_dir <- paste0("C:/Users/", username, "/Desktop/Factbook_visualizations/")
output_dir <- "O:/OIRA/Factbook/" # Where output files should reside
photo_shelter_dir <- paste0(output_dir, "NCCU_photo_shelter/") # directory specifying photo shelter files
university_finances_dir <- paste0(output_dir, "University_Finances/") # directory specifying university finance reports
tuition_pdf_file <- paste0("O:/OIRA/IR/Tuition and Fees/", year, "-", year+1, "-Approved-Tuition-and-Fees-Schedule.pdf") # file path of PDF document
overwrite <- "yes" # yes or no. Yes will remove all output/intermediary folders for specified year and start over

NCCU_maroon <- "#862633"
NCCU_gray <- "#A2AAAD"
bg_color <- "#e5dfca"
rich_maroon <- "#6A2C3E"
black <- "#000"
font_type <- "Calibri"

```



# Pass variables to individual FactBook section scripts for execution
```{r, warning=FALSE, message=FALSE}

# 1). Before we begin anything, need to ensure Chrome browser is installed, otherwise won't work and need to install Chrome
if (is.null(pagedown::find_chrome())) {
  message("Chrome browser not found on this system, which must be installed to execute this program. Terminating now...")
}


# 2). Source file containing collection of functions, and load necessary packages
source(paste0(output_dir, "FactBook_functions.R"))
load_packages()


# 3). Set a few things up
if (overwrite == "yes") {
  if (file.exists(paste0(output_dir, "Factbook_", year, "-", year+1))) {
    dir_delete(paste0(output_dir, "Factbook_", year, "-", year+1))
  }
  if (file.exists(intermediary_dir)) {
    dir_delete(intermediary_dir)
  }
}

if (!file.exists(intermediary_dir)) {
    dir.create(intermediary_dir)
}

if (!file.exists(output_dir)) {
    dir.create(output_dir)
}

if (dir.exists(paste0(output_dir, "Factbook_visualizations"))) {
  unlink(paste0(output_dir, "Factbook_visualizations"), recursive = TRUE)
}


# 3). Convert all NCCU photo shelter JPEG pictures to HTML format (if necessary)
jpg_to_html_convert(photo_shelter_dir)


# 4). Copy oira_gradret.txt file into data_dir
file.copy("W:/Source/oira_gradret.txt", data_dir)


# 5). Create parameter list that will be passed to individual FactBook section scripts for execution
params_list <- list(
  section_id = "s1", # default value
  section = "", # default value
  year = year,
  data_dir = data_dir,
  intermediary_dir = intermediary_dir,
  output_dir = output_dir,
  photo_shelter_dir = photo_shelter_dir,
  NCCU_maroon = NCCU_maroon,
  NCCU_gray = NCCU_gray,
  font_type = font_type,
  bg_color = bg_color,
  rich_maroon = rich_maroon,
  black = black
)


# 6). # Create information list 
section_info_list <- list(
  list(section_id = "s1", section = "General Information", script = "Factbook_generation_General_Information.R", dashboard_url = ""),
  list(section_id = "s1", section = "Eagle Facts in Brief", script = "", dashboard_url = ""),
  list(section_id = "s2", section = "New Student", script = "Factbook_generation_New_Student.R", dashboard_url = "https://www.nccu.edu/oira/dashboards-institutional-data/admissions-dashboard"),
  list(section_id = "s3", section = "Fall Enrollment", script = "Factbook_generation_Fall_Enrollment.R", dashboard_url = "https://www.nccu.edu/oira/dashboards-institutional-data/enrollment-dashboard"),
  list(section_id = "s4", section = "Degrees Awarded", script = "Factbook_generation_Degrees_Awarded.R", dashboard_url = "https://www.nccu.edu/oira/dashboards-institutional-data/nccu-degrees-awarded-dashboard"),
  list(section_id = "s5", section = "Student Financial Aid", script = "Factbook_generation_Student_Financial_Aid.R", dashboard_url = "https://www.nccu.edu/oira/dashboards-institutional-data/financial-aid"),
  list(section_id = "s6", section = "Employees", script = "Factbook_generation_Employees.R", dashboard_url = "https://www.nccu.edu/oira/dashboards-institutional-data/nccu-employment"),
  list(section_id = "s7", section = "University Finances", script = "Factbook_generation_University_Finances.R", dashboard_url = ""),
  list(section_id = "s8", section = "End of Document", script = "", dashboard_url = ""),
  list(section_id = "s9", section = "HTML-to-PDF conversion", script = "Factbook_generation_HTML_to_PDF.R", dashboard_url = "")
)


# 7). Execute Fact Book sections code
generate_main_title_page(year, intermediary_dir, photo_shelter_dir, bg_color)

for (section_info in section_info_list) {

  if (!section_info$section_id == "s9") {
    # Generate section title HTML pages
    generate_section_title_page(section_info, intermediary_dir, bg_color, section_info$section)
  }
  
  if (!(section_info$section_id == "s8") & !(section_info$section == "Eagle Facts in Brief")) {
    # Update parameters and environment for code execution
    params_list$section_id <- section_info$section_id
    params_list$section <- section_info$section
  
    list2env(params_list, envir = globalenv())
  
    print("")
    print("-----------------------------------")
    print(paste0("Execution section: ", section_info$section))
    print("-----------------------------------")
    source(paste0(output_dir, section_info$script), echo = FALSE)
  }
}


# 8). Once all sections have finished, move the intermediary locations visualizations to the output directory
print("Moving intermediary directory contents to output directory")
old_path <- intermediary_dir
new_path <- paste0(output_dir, "Factbook_", year, "-", year+1)

dir_copy(old_path, new_path, overwrite = TRUE)
dir_delete(old_path)

print(paste0("Completed FactBook ", year, "-", year+1, " generation"))

```